---
title: "Palmer_Penguins"
author: "Sukh Singh"
date: "24/04/2021"
output: html_document
---

## Setting up my environment
Notes: Setting up my R environment by loading the 'tidyverse' and 'palmer 
penguins' packages

```{r Loading Packages}
library(tidyverse)
library(palmerpenguins) 
library(ggplot2)
```
```{r Fipper vs body mass by species, warning=FALSE}
ggplot(data=penguins) +
  geom_point(mapping = aes(x=flipper_length_mm, y=body_mass_g, color=species)) +
  labs(title="Palmer Penguins: Body Mass v/s Flipper Length",
       subtitle="Sample of three species",
       caption="Data collected by Dr. Kristen Gormen") +
  annotate("text", x= 215, y= 3500, label= "Gentoo's are the largest")
```

The graph above has a Title, Subtitle, Caption and a Text annotation identifying 
the largest species.
```{r A curved reation between Flipper Length and Body Weight, warning=FALSE}
ggplot(data=penguins) +
  geom_point(mapping=aes(x=flipper_length_mm, y=body_mass_g), color = "blue") +
  geom_smooth(mapping=aes(x=flipper_length_mm, y=body_mass_g), color = "red") +
  labs(title = "Flipper Length v/s Body Mass - Curved Relation",
       caption = "Data collected by Dr. Kristen Gormen")
```

## Using Facet
The following graph shows the relation of flipper length and body mass 
with regards to the sex of penguins.

```{r A facet graph of Flipper Lenght v/s Body Mass w.r.t. sex, warning=FALSE}
ggplot(data=penguins)+
  geom_point(mapping = aes(x= flipper_length_mm, y= body_mass_g, color= species))+
  facet_grid(sex~species)+
  labs(title= "Flipper Length v/s Body Mass w.r.t Sex")

```

## Conclusion
The analysis above clearly states that regardless of the sex, a penguin's flipper length increases as the body mass goes up. This means that penguins grow larger in all aspects.
